Colonies - Compute Continuums across Platforms

### 2023-03-29 paper_2023/paper.tex
wip

The paper also describes how Colonies can be used to build a scalable remote sensing platform on Kubernetes, how it can be used as a building block for edge computing, and how it can be integrated with HPC platforms. Finally, the paper presents a performance investigation as well as a scalability and robustness evaluation. 
\end{abstract}

@@

\section{Introduction}
Building robust and scalable AI systems is challenging and requires deep understanding in various fields. First an AI model must be trained, requiring technical skills in advanced statistics or machine learning, but also access to training and validation data. Usually, the data need to be pre-processed in several steps before it can be used, or a simulator needs to be developed to either generate syntentic data or play back historical data. While it may be resonable for small scale projects to run a whole environment on a local development computer, training large AI models usually requires access to powerful compute clusters or even HPC systems. Manually utilizing such infrastructure is cumbersome and time consuming. Being able to automate the training processes makes it possible to more quickly iterate and find useful models.

Going forward and taking an AI model into production requires significant software engineering skills. In constract to traditional IT workloads both the data and the model itself need to be managed. As most models need to be re-trained or re-calibrated regularly, it muste be possible to seamlessly update deployed model and the software without loosing information or introducing delays. In many cases, there is a constant flow of data that is ingested into the system that needs to be managed while parts of the system is not working correctly. This becomes even more challenging when nodes parts of the underlying infrastructure crashes or becomes unavailable due to maintenance such as software updates or misconfiguration errors.

Sometimes there is also need to scale the system to increase capacity or scale down to save resources. This is particularly important when using expensive cloud resources. Scaling the system means that underlying infastructure may change anytime causing additional failures. It must therefor be possible to detected failed computations and re-process failed tasks part of a larger workflow. If failed computation cannot gracefully be recovered, there must be a away for engineers perform root cause analysis and manually recover failures.

>>>>

In additional to a technical description, the paper also describes how Colonies can be used to build a scalable remote sensing platform on Kubernetes, how it can be used as a building block for edge computing, and how it can be integrated with HPC platforms. Finally, the paper presents a performance investigation as well as a scalability and robustness evaluation. 
\end{abstract}

@@

\section{Introduction}
Building robust and scalable AI systems is challenging and requires a deep understanding of various fields. Firstly, an AI model must be trained, which requires technical skills in advanced statistics or machine learning, as well as access to training and validation data. Usually, the data needs to be pre-processed in several steps before it can be used, or a simulator needs to be developed to generate synthetic data or play back historical data. While it may be reasonable for small-scale projects to run the whole environment on local development computers, training larger AI models usually requires access to powerful compute clusters or even HPC systems. Manually utilizing such infrastructure is cumbersome and time-consuming. Automating the training processes makes it possible to iterate more quickly and find useful models.

Going forward and taking an AI model into production requires significant software engineering skills. In contrast to traditional IT workloads, both the data and the model itself need to be managed. As most models need to be re-trained or re-calibrated regularly, it must be possible to seamlessly update the deployed model and the software without losing information or introducing delays. In many cases, there is a constant flow of data that is ingested into the system that needs to be managed while parts of the system are not working correctly. This becomes even more challenging when nodes or parts of the underlying infrastructure crash or become unavailable due to maintenance, such as software updates or misconfiguration errors.

Sometimes there is also need to scale the system to increase capacity or scale down to save resources. This is particularly important when using expensive cloud resources. Scaling the system means that underlying infastructure may change anytime causing instability problems for running applications. It must therefor be possible to detected failed computations and re-process failed tasks part of a larger workflow. Running workflows must therefor be designed to handle an ever changing infrastructure, and if a failed computation cannot gracefully be restored, there must be a away for engineers perform root cause analysis and manually recover failures.

In reality, several systems must be integrated to build fully working AI applications. For example, data might must be captured from an IoT system or pulled from third-party services running on different domains than the compute cluster. With the introduction of edge computing, parts of the data pipeline might also execute on edge servers, or even in on devices to bring computation closer where the data is produced. Configuring and setting up such pipelines adds further complexity.

In addition, many compute clusters run on-prem and somtimes there is a need to temporary increase the capacity by mixing on-prem and cloud resources, for example to handle peek load or re-process historical data. This also requires integration of various security protocols to provision and . Creating hybrid workflows where some jobs run on HPC systems requires even more software development efforts and is out of the scope for many users, preventing them from utilizing powerful hardware. Clearly, there is a need for a framework that can consolidate various platforms to simplify development and allowing computations to seamlessly run across platforms.

This paper presents a loosly coupled microservice inspired architecuture that seperates workflow definitions from implementation and deployment. The ultimate goal is to create an architecuture where monolitic workflows are broken down into independent and seperated compute units, which can be dynamically added or removed to running workflows. These compute units could then be implemented in any computer language and be deployed anywhere on the Internet. The paper describes a framework called Colonies implementing such an architecutre. The paper describes several use cases
